Methodology for Assessing the State of the Practice for Domain X

### 2020-11-06 StateOfPractice/Methodology/Methodology.tex
updated section 2 research questions, methodology, refs to questions to devs

\pmi{comment from meeting: remove performance benchmarks from scope of exercise because enough other people consider this. Add similar comment into introduction explaining (link to examples of performance considered elsewhere in similar projects??) why performance is not considered}
\pmi{do we have specific examples of other people considering performance benchmarks?}

@@

\begin{enumerate}
\item What are the artifacts that current software packages consist of? 
\item What tools are used by current software packages?
\item What principles, processes, and methodologies are used in the development of current software packages?
\item What are the pain points for developers working on SCS projects? What aspects of the existing processes, methodologies and tools do they consider could potentially be improved? What processes, methodologies and tools have they changed to reduce obstacles?
\item For research software developers, what specific actions are taken to address the following:
\begin{enumerate}
\item usability \pmi{question 10 touches on this but will need to be reworded or broken up - ``What if any actions were taken to address usability issues?''}
\item traceability \pmi{question to developers 3}
\item modifiability \pmi{question to developers 9}
\item maintainability \pmi{question to developers 9}
\item correctness \pmi{question to developers 8}
\item understandability \pmi{question to developers 10 touches on this; need to reword question in terms of an action}
\item unambiguity \pmi{question to developers 11}
\item reproducibility \pmi{question to developers 12}
\item visibility/transparency \pmi{questions 1,3,4,5,6 build to this but a question would need to be modified to include something along the line of ``has this information been added to the documentation?''}
\end{enumerate} 
\item How does software designated as high quality by this methodology compare with top rated software by the community? \pmi{review}
\end{enumerate}

>>>>

\pmi{comment from meeting: remove performance benchmarks from scope of exercise because enough other people consider this. Add similar comment into introduction explaining (link to examples of performance considered elsewhere in similar projects??) why performance is not considered}
\pmi{do we have specific examples of other works considering performance benchmarks?}

@@

\begin{enumerate}
\item What are the artifacts that current software packages consist of? 
\item What tools are used by current software packages?
\item What principles, processes, and methodologies are used in the development of current software packages?
\item What are the pain points for developers working on SCS projects? What aspects of the existing processes, methodologies and tools do they consider could potentially be improved? What processes, methodologies and tools have they changed to reduce obstacles?
\item For research software developers, what specific actions are taken to address the following:
\begin{enumerate}
\item usability \pmi{question to developers 11}
\item traceability \pmi{question to developers 3}
\item modifiability \pmi{question to developers 9}
\item maintainability \pmi{question to developers 9}
\item correctness \pmi{question to developers 8}
\item understandability \pmi{question to developers 10}
\item unambiguity \pmi{question to developers 12}
\item reproducibility \pmi{question to developers 13}
\item visibility/transparency \pmi{question to developers 3}
\end{enumerate} 
\item How does software designated as high quality by this methodology compare with top rated software by the community?
\end{enumerate}
